\Large \bf A first look at auditing in a blockchain world

### 2018-09-26 auditing/Latex/main.tex
[auditing] transition to Latex. till Section 3
Audit clean up
More draft-like (needs ack from JMSB people)

\input{setup/packages}
\input{setup/macros}
\input{setup/table}

% = = = = = Title = = = = = %

@@

\title{The paper on \Large \bf Blockchain Frontrunning}
%\author{}

%\author{}
\institute{Concordia University}

@@

\input{sections/abstract}

@@

\input{sections/paper}

@@

\bibliography{bib/Frontrunning_Ref}
%\nocite{*}

>>>>

\input{setup/packages}
\input{setup/macros}
\usepackage{draftwatermark}
\SetWatermarkAngle{90}
\SetWatermarkHorCenter{0.2\textwidth}
\SetWatermarkColor{blue}
\SetWatermarkText{Working Draft}
% = = = = = Title = = = = = %

@@

\title{\Large \bf A first look at auditing in a blockchain world}

\author{
	Erica Pimentel\inst{1},
	Emilio Boulianne\inst{1},
	Shayan Eskandari\inst{2},
	Jeremy Clark\inst{2}
	}

\institute{
	\textsuperscript{1} John Molson School of Business,
	\textsuperscript{2} Gina Cody School of Engineering and Computer Science\\ Concordia University
	}

@@

\input{sections/00-abstract}

@@

\input{sections/01-intro}
\input{sections/02-body}

@@

\section{Acknowledgements}

The authors thank the Autorit\'e des March\'es Financiers (AMF) for sponsoring this research through the Education and Good Governance Fund (EGGF).

\bibliography{bib/auditing}
%\nocite{*}
